---
title: "Trends"
author: "Mike Wessel"
date: "6/19/2021"
output:
  html_document: default
  pdf_document: default
---


```{r , include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## NOTE: THIS IS AN EXPERIENTAL TEST SITE AND IS NOT TO BE INTERPRETED AS A FINAL RESULT

## Background

These maps display results of Seasonal Kendall Tau trend test with autocorrelation on Pinellas County water quality data and uses the Benjamini and Hochberg method to adjust for multiple comparions within each water quality parameter set. 
```{r setup, message = FALSE}
## Load Libraries
library(tidyverse)
library(dplyr)
library(sf)
library(ggspatial) # north arrow and scale bar for map
library(mapview)
library(leaflet)
library(webshot)
#install.packages("webshot")
#webshot::install_phantomjs()
#tinytex::install_tinytex()


```



```{r}
# get working directory
getwd() 

# Clear workspace 
rm(list = ls())
```
## Total Nitrogen Map Results

```{r tn}
#  Read in Trend results from trend tests

PC_trends_full_join<- readRDS(file = "PC_trends_full_join.Rds")
trends<-PC_trends_full_join  


 m<-trends%>%
    filter(stas=="TN")%>%
      mutate( Group = case_when(
    final_est == "Not" ~ 1,
    final_est == "Increasing" ~ 2,
    final_est == "Decreasing" ~ 3),
        icon = case_when(
         Group == 1 ~ "cog",
         Group == 2 ~ "arrow-up",
         Group == 3 ~ "arrow-down"),
        )

# https://fontawesome.com/v5.15/icons?d=gallery&p=3
# create awesome icons
my_icons <- awesomeIcons(icon = m$icon, library = "glyphicon")
 
 
  mm<- leaflet(m)%>%
      addProviderTiles(providers$OpenStreetMap) %>%
   #   addCircleMarkers(lng = ~ Longitude, lat = ~ Latitude, color = "blue", fillColor = "blue", opacity = 0.5, radius = 15, fillOpacity = 0.5) %>% 
      addAwesomeMarkers(lng = ~ Longitude, lat = ~ Latitude, icon = ~ my_icons[Group],            popup=~as.character(grand_med),label = ~as.character(grand_med) )
     
 mm
 
 # to get rid of pin marker i think you need to specify an html makrer
 # https://rstudio.github.io/leaflet/markers.html
 
 # or look at this and download PhantomJS
 # https://www.earthdatascience.org/courses/earth-analytics/get-data-using-apis/leaflet-r/

```
 
 
## Chlorophyll a Map Results

```{r chla}
#  Read in Trend results from trend tests

PC_trends_full_join<- readRDS(file = "PC_trends_full_join.Rds")
trends<-PC_trends_full_join  


 m<-trends%>%
    filter(stas=="Chl_a")%>%
      mutate( Group = case_when(
    final_est == "Not" ~ 1,
    final_est == "Increasing" ~ 2,
    final_est == "Decreasing" ~ 3),
        icon = case_when(
         Group == 1 ~ "cog",
         Group == 2 ~ "arrow-up",
         Group == 3 ~ "arrow-down"),
        )

# https://fontawesome.com/v5.15/icons?d=gallery&p=3
# create awesome icons
my_icons <- awesomeIcons(icon = m$icon, library = "glyphicon")
 
 
  mm<- leaflet(m)%>%
      addProviderTiles(providers$OpenStreetMap) %>%
   #   addCircleMarkers(lng = ~ Longitude, lat = ~ Latitude, color = "blue", fillColor = "blue", opacity = 0.5, radius = 15, fillOpacity = 0.5) %>% 
      addAwesomeMarkers(lng = ~ Longitude, lat = ~ Latitude, icon = ~ my_icons[Group],            popup=~as.character(grand_med),label = ~as.character(grand_med) )
     
 mm
 
 # to get rid of pin marker i think you need to specify an html makrer
 # https://rstudio.github.io/leaflet/markers.html
 
 # or look at this and download PhantomJS
 # https://www.earthdatascience.org/courses/earth-analytics/get-data-using-apis/leaflet-r/

```